---
title: 'Linear models: exercises'
author: "Stefano Coretta"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.width = 7, fig.height = 5, out.height = "500px", fig.align = "center")
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_minimal(base_size = 16))
library(lme4)
library(ggeffects)
library(broom.mixed)
options(ggplot2.discrete.colour = RColorBrewer::brewer.pal(5, "Dark2"))
options(show.signif.stars = FALSE)
```

# Read data

```{r shallow}
shallow <- read_csv("04-fit-models/shallow-morph.csv") %>%
  filter(Critical_Filler == "Critical") %>%
  mutate(
    Relation_type = factor(Relation_type, levels = c("Unrelated", "Constituent", "NonConstituent"))
  )
```

# Summarise the data

Calculate summary statistics.







# Plot the data

Create a variety of plots to show patterns (or absence thereof).






# Model the data with linear models

Let's first try with a simple model.

```{r shallow-lm-1}
shallow_lm_1 <- glmer(
  ACC ~ Relation_type + (Relation_type | ID),
  data = shallow,
  family = binomial()
)
```

Did it work?

```{r shallow-lm-2}
shallow_lm_2 <- glmer(
  ACC ~ Relation_type + (1 | ID),
  data = shallow,
  family = binomial()
)
```

Did it work?

If it did work, print the summary with `summary()` and try to interpret the coefficients.







Then plot the model with `ggpredict()` from the ggeffects package (see slides from `04-fit-models`).





Now run the model again but include the predictor `Group`. Shall you include an interaction with `Relation_type` too?






Now try to write up the results of the two last models.
