---
title: "Linear models: Reporting"
author: "Stefano Coretta"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css:
      - default
      - ../ipa-fonts.css
      - ../custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "../macros.js"
      ratio: 16:9
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.width = 7, fig.height = 5, out.height = "500px", fig.align = "center")
knitr::opts_knit$set(root.dir = here::here())
options(htmltools.dir.version = FALSE)
library(tidyverse)
theme_set(theme_minimal(base_size = 16))
options(ggplot2.discrete.colour = RColorBrewer::brewer.pal(5, "Dark2"))
library(xaringanExtra)
use_xaringan_extra(c("panelset", "tachyons"))
library(ggeffects)
options(show.signif.stars = FALSE)
library(lme4)
library(broom.mixed)
```

```{r read-data}
shallow <- read_csv("04-fit-models/shallow-morph.csv") %>%
  filter(Critical_Filler == "Critical") %>%
  mutate(
    Relation_type = factor(Relation_type, levels = c("Unrelated", "Constituent", "NonConstituent"))
  )
```


# Reporting model specifications

```{r shallow-lm-2, echo=TRUE}
shallow_lm_2 <- glmer(ACC ~ Relation_type * Group + (1 | ID), data = shallow, family = binomial())

summary(shallow_lm_2)
```

---

# Reporting model specifications

```{r shallow-lm-2-2, echo=TRUE, eval=FALSE}
shallow_lm_2 <- glmer(ACC ~ Relation_type * Group + (1 | ID), data = shallow, family = binomial())

summary(shallow_lm_2)
```

We fitted a linear model with lme4 (Bates et al. 2015) in R 4.1.2 (R Core Team 2021), using a Bernoulli distribution family (aka logistic regression, binomial regression).
As predictors, we included Relation Type (Unrelated, Constituent, Nonconstituent), Group (L1, L2), and an interaction between the two.
Both predictors were coded using treatment contrasts (aka dummy coding), with the first level as the reference level.
We also included a by-participant random intercept (we tried also including a by-participant random slope for Relation Type, but the model failed to converge).

---

# Reporting model results

```{r shallow-lm-2-3, echo=FALSE}
tidy(shallow_lm_2, effects = "fixed")
```

According to the linear model fitted to the accuracy data, native speakers show 85% accuracy (`\(\beta = 1.746\)`, $SE=0.196$, $z=8.892$, $p < 0.0001$) when the relation type is Unrelated, 91% accuracy (`\(\beta=0.606\)`, $SE=0.231$, $z=2.624$, $p = 0.00869$) with Constituent type, and 78% accuracy when the type is Nonconstituent (`\(\beta=-0.459\)`, $SE=0.234$, $z=1.958$, $p = 0.05011$).
The estimates for the non-native group indicates that they don't significantly differ from those of native (see Table X for the model output.)
